---
title: 'Ideological Identification in Cyprus'
author: 'Yioryos Nardis'
date: '2019-12-16'
slug: ideological-identification
categories: []
tags:
  - politics
subtitle: ''
description: ''
image: ''
---


```{r setup, eval=FALSE, echo=FALSE}
library(haven)
library(labelled)
library(survey)
library(dplyr)
library(tidyr)
library(stats)
library(Hmisc)
library(car)
library(sjmisc)

knitr::opts_knit$set(root.dir = '')


#Access Eurobarometer data files from websites of EU Open Data Portal, ICPSR, or GESIS
load("EB2004.62.rdata")
load("EB2005.63.4.rdata")
load("EB2006.65.2.rdata")
load("EB2007.68.1.rdata")
load("EB2008.70.1.rdata")
load("EB2009.71.3.rdata")
load("EB2010.74.2.rdata")
load("EB2011.75.3.rdata")
load("EB2014.81.4.rdata")
load("EB2015.84.3.rdata")
load("EB2016.85.2.rdata")
load("EB2017.87.3.rdata")
load("EB2018.90.3.rdata")

#####Recoding variables for 2018 dataframe#####  
#Country variables
EB2018.90.3$country1 <- car::recode(EB2018.90.3$country, as.factor = T, "'1' = 'France'; '2' = 'Belgium'; '3' = 'Netherlands';
'5' = 'Italy'; '6' = 'Luxembourg'; '7' = 'Denmark'; '8' = 'Ireland'; '9' = 'UK';
'11' = 'Greece'; '12' = 'Spain'; '13' = 'Portugal'; '16' = 'Finland'; '17' = 'Sweden';
'18' = 'Austria'; '20' = 'Czech Republic'; '21' = 'Estonia'; '22' = 'Hungary';
'23' = 'Latvia'; '24' = 'Lithuania'; '25' = 'Malta'; '26' = 'Poland'; '27' = 'Slovakia'; 
'28' = 'Slovenia'; '29' = 'Bulgaria'; '30' = 'Romania'; else = NA")

EB2018.90.3$germany <- car::recode(EB2018.90.3$country, as.factor = T, "'4' = 'W Germany'; '14' = 'E Germany'; else = NA") 
EB2018.90.3$germany <- car::recode(EB2018.90.3$germany, as.factor = T, "'W Germany' = 'Germany'; 'E Germany' = 'Germany'; else = NA") 
EB2018.90.3$cyprus <- car::recode(EB2018.90.3$country, as.factor = T, "'19' = 'Greek-Cypriots'; '33' = 'Turkish-Cypriots'; else = NA")

EB2018.90.3$country2 <- car::recode(EB2018.90.3$country, as.factor = T, "'1' = 'France'; '2' = 'Belgium'; '3' = 'Netherlands';
'5' = 'Italy'; '6' = 'Luxembourg'; '7' = 'Denmark'; '8' = 'Ireland'; '9' = 'UK';
'11' = 'Greece'; '12' = 'Spain'; '13' = 'Portugal'; '16' = 'Finland'; '17' = 'Sweden';
'18' = 'Austria'; '19' = 'GCC'; '20' = 'Czech Republic'; '21' = 'Estonia'; '22' = 'Hungary';
'23' = 'Latvia'; '24' = 'Lithuania'; '25' = 'Malta'; '26' = 'Poland'; '27' = 'Slovakia'; 
'28' = 'Slovenia'; '29' = 'Bulgaria'; '30' = 'Romania'; '33' = 'TCC'")

#EU-28 indicator variable
table(EB2018.90.3$eu28)
EB2018.90.3$eu28 <- as.factor(EB2018.90.3$eu28)
str(EB2018.90.3$eu28)

#10-point left-right ideology variable
describe(EB2018.90.3$d1)
EB2018.90.3$d1_rec <- as.numeric(EB2018.90.3$d1)
EB2018.90.3$d1_rec[EB2018.90.3$d1_rec > 10] <- NA
str(EB2018.90.3$d1_rec)
describe(EB2018.90.3$d1_rec)

#Gender
#Male=1; Female=2
describe(EB2018.90.3$d10)
EB2018.90.3$d10_fac <- as.factor(EB2018.90.3$d10)
EB2018.90.3$d10_fac <-
  recode_factor(EB2018.90.3$d10_fac, '1' = "Male", '2' = "Female")
describe(EB2018.90.3$d10_fac)
str(EB2018.90.3$d10_fac)

save(EB2018.90.3, file=("EB2018.90.3.rdata"))



#####Functions to calculate weighted survey estimates

#Fuction passing lists of data, weight, group and trust measure into 'survey' package
Func <- function(passedData, passedWeights, group, estimate, groupVal){
  EBsurvey <- svydesign(strata = NULL, ids = ~0, weights = passedData[, passedWeights], data = passedData)
  EBsurveySubset <- subset(EBsurvey, EBsurvey[["variables"]][,group] == groupVal)
  result <- svymean(as.formula(paste0("~", estimate)), EBsurveySubset, na.rm=TRUE)
  return(result)
}


#First function calling 'Func'. Calcuates weighted survey estimates for one factor level of given measure by group and subgroup (GCC/TCC) across time
applyFunc  <- function(varName, groupVal, dataInfo)
{
  results <- data.frame(rep(NA, length(dataInfo)))
  colnames(results) <- varName
  for(i in 1:nrow(results)) {
    results[i,varName] <- Func(dataInfo[[i]]$passedData, dataInfo[[i]]$passedWeights, dataInfo[[i]]$group, dataInfo[[i]]$estimate, groupVal)[[1]] 
  }
  return(results)
}


#Second function calling 'Func'. Calcuates weighted survey estimates for multiple factor levels of given measure by group and subgroup (GCC/TCC) across time
applyFunc2  <- function(groupVal, dataInfo)
{
  results <- data.frame(rep(NA, length(dataInfo),))
  for(i in 1:nrow(results)) {
    for(j in 1:4) {
      results[j, i] <- Func(dataInfo[[i]]$passedData, dataInfo[[i]]$passedWeights, dataInfo[[i]]$group, dataInfo[[i]]$estimate, groupVal)[[j]] 
    }}
  return(results)
}


#Function to convert to percentages
mult_one <- function(var1)
{
  round((var1*100), 1) 
}



######Analysis 1: Cyprus vs EU in 2018
#Lists with data, weights, groups and variables to pass into survey estimate function

id1 <- list(passedData = EB2018.90.3, passedWeights="w1", group="cyprus", estimate="d1_rec") #Cyprus
id2 <- list(passedData = EB2018.90.3, passedWeights="w3", group="germany", estimate="d1_rec") #Germany
id3 <- list(passedData = EB2018.90.3, passedWeights="w23", group="eu28", estimate="d1_rec") #EU-28


#Calculating Left-Right Ideology mean
dataInfo <- list(id1)
ideology <- applyFunc("ideology_gcc", "Greek-Cypriots", dataInfo) #GCC

dataInfo <- list(id1)
results <- applyFunc("ideology_tcc", "Turkish-Cypriots", dataInfo) #TCC
ideology <- cbind(ideology, results)

dataInfo <- list(id2)
results <- applyFunc("ideology_ger", "Germany", dataInfo) #Germany
ideology <- cbind(ideology, results)

dataInfo <- list(id3)
results <- applyFunc("ideology_eu28", "1", dataInfo) #EU-28
ideology <- cbind(ideology, results)


#Reshaping from wide to long
ideology <- ideology %>% gather(group, ideology, ideology_gcc:ideology_eu28)

ideology$group <- dplyr::recode(ideology$group, "ideology_gcc" = "Greek-Cypriots", "ideology_tcc" = "Turkish-Cypriots", "ideology_ger" = "Germany", "ideology_eu28" = "EU-28")


#Calculating combined Cypriot means using population estimates from technical specifications in Eurobarometer codebooks
ideology$weight <-c(741308/884534, 143226/884534, NA, NA)
ideology <- ideology %>% mutate(ideology_w = ideology * weight)

ideology_cyp <- ideology %>% filter(group == "Greek-Cypriots" | group == "Turkish-Cypriots")
ideology_cyp <- ideology_cyp %>% select(-"ideology", -"weight")

ideology_cyp <- ideology_cyp %>% 
  summarise(ideology = sum(ideology_w))

ideology_cyp$group <- c("Cyprus (GCC & TCC)")
ideology <- ideology %>% select(-"ideology_w", -"weight")
ideology <- rbind(ideology, ideology_cyp)


#Calculating left-right ideology mean for all EU apart from Cyprus & Germany
#Adding EB complex survey design & calculating ideology
EB2018.90.3_svy <- svydesign(strata = NULL, ids = ~0, weights = ~w1, data = EB2018.90.3)
EU_count <- svyby(~d1_rec, ~country1, EB2018.90.3_svy, svymean, se=F, na.rm=T, ci=F, keep.names=F)

EU_count <- as.data.frame(EU_count)
EU_count <- EU_count %>% select(-"se")
EU_count <- EU_count %>% rename(group = country1, ideology = d1_rec) 

#Dataframe with all groups
ideology_all <- rbind(ideology, EU_count)
ideology_all$ideology <- round(ideology_all$ideology, 1) 
ideology_all$group <- factor(ideology_all$group, levels = ideology_all$group) 

#Dataframe for Cyprus commnuities & EU-28
ideology_cyp <- ideology_all %>% filter(group == "Greek-Cypriots" | group == "Turkish-Cypriots" | group == "Cyprus" | group == "EU-28")

#Dataframe for groups without separate Cyprus communities
ideology_eu <- ideology_all %>% filter(group != "Greek-Cypriots" & group != "Turkish-Cypriots" & group != "EU-28")


######Analysis 2: Calculating left-right ideology by gender for Cyprus and EU-28
gcc <- EB2018.90.3 %>% filter(cyprus == "Greek-Cypriots")
tcc <- EB2018.90.3 %>% filter(cyprus == "Turkish-Cypriots")

EB2018.90.3_gcc_svy <- svydesign(strata = NULL, ids = ~0, weights = ~w1, data = gcc)
gcc_gen <- svyby(~d1_rec, ~d10_fac, EB2018.90.3_gcc_svy, svymean, se=F, na.rm=T, ci=F, keep.names=F)
gcc_gen$group <- "Greek-Cypriots"

EB2018.90.3_tcc_svy <- svydesign(strata = NULL, ids = ~0, weights = ~w1, data = tcc)
tcc_gen <- svyby(~d1_rec, ~d10_fac, EB2018.90.3_tcc_svy, svymean, se=F, na.rm=T, ci=F, keep.names=F)
tcc_gen$group <- "Turkish-Cypriots"

EB2018.90.3_eu_svy <- svydesign(strata = NULL, ids = ~0, weights = ~w23, data = EB2018.90.3)
eu28_gen <- svyby(~d1_rec, ~~d10_fac, EB2018.90.3_eu_svy, svymean, se=F, na.rm=T, ci=F, keep.names=F)
eu28_gen$group <- "EU-28"

ideology_gen <- as.data.frame(rbind(gcc_gen, tcc_gen, eu28_gen))
ideology_gen <- ideology_gen %>% rename(gender = d10_fac, ideology = d1_rec) 
ideology_gen$ideology <- round(ideology_gen$ideology, 1) 
ideology_gen$se <- round(ideology_gen$se, 2) 
ideology_gen <- ideology_gen %>% mutate(group = factor(group, levels = c("EU-28", "Turkish-Cypriots", "Greek-Cypriots")))
ideology_gen <- ideology_gen %>% mutate(gender = factor(gender, levels = c("Female", "Male")))

save(ideology_gen, file=("ideology_gen.rdata"))
save(ideology_eu, file=("ideology_eu.rdata"))


######Analysis 3: Left-right ideology categories over time for Cyprus
#No data for Turkish Cypriots, 2012-2013

#Lists with data, weights, groups and variables to pass into survey estimate function
id4 <- list(passedData = EB2004.62, passedWeights="V8", group="V6", estimate="V423_fac")
id5 <- list(passedData = EB2005.63.4, passedWeights="V8", group="V6", estimate="V405_fac")
id6 <- list(passedData = EB2006.65.2, passedWeights="V8", group="V6", estimate="V3305_fac")
id7 <- list(passedData = EB2007.68.1, passedWeights="V8", group="V6", estimate="V415_fac")
id8 <- list(passedData = EB2008.70.1, passedWeights="V8", group="V6", estimate="V665_fac")
id9 <- list(passedData = EB2009.71.3, passedWeights="W1", group="COUNTRY", estimate="D1R1_fac")
id10 <- list(passedData = EB2010.74.2, passedWeights="V8", group="V6", estimate="V595_fac")
id11 <- list(passedData = EB2011.75.3, passedWeights="v8", group="v6", estimate="v608_fac")
id12 <- list(passedData = EB2014.81.4, passedWeights="W1", group="COUNTRY", estimate="D1R1_fac")
id13 <- list(passedData = EB2015.84.3, passedWeights="W1", group="COUNTRY", estimate="D1R1_fac")
id14 <- list(passedData = EB2016.85.2, passedWeights="W1", group="COUNTRY", estimate="D1R1_fac")
id15 <- list(passedData = EB2017.87.3, passedWeights="W1", group="COUNTRY", estimate="D1R1_fac")
id16 <- list(passedData = EB2018.90.3, passedWeights="w1", group="country2", estimate="d1r1_fac")



#####Calculating Left-Right Ideology Groups
#Cyprus
dataInfo <- list(id4, id5, id6, id7, id8, id9, id10, id11, id12, id13, id14, id15, id16) 
results_gcc <- applyFunc2("GCC", dataInfo)
results_gcc <- results_gcc[1:4,]
colnames(results_gcc)<- c("GCC_2004","GCC_2005","GCC_2006","GCC_2007","GCC_2008","GCC_2009","GCC_2010","GCC_2011","GCC_2014","GCC_2015","GCC_2016","GCC_2017","GCC_2018")

results_tcc <- applyFunc2("TCC", dataInfo)
results_tcc <- results_tcc[1:4,]
colnames(results_tcc)<- c("TCC_2004","TCC_2005","TCC_2006","TCC_2007","TCC_2008","TCC_2009","TCC_2010","TCC_2011","TCC_2014","TCC_2015","TCC_2016","TCC_2017","TCC_2018")

ideo_cat <- cbind(results_gcc, results_tcc)
ideo_cat <- mapply(mult_one,ideo_cat)
ideo_cat <- as.data.frame(ideo_cat)

ideo_cat<- ideo_cat %>% gather()
ideo_cat$ideology <- c("Left", "Centre", "Right", " Don't Know")
ideo_cat$ideology <- as.factor(ideo_cat$ideology)

#Creating year and Cyprus group variables
ideo_cat$year <- ideo_cat$key
ideo_cat$year <- gsub("GCC_", "", ideo_cat$year)
ideo_cat$year <- gsub("TCC_", "", ideo_cat$year)
ideo_cat$year <- as.numeric(ideo_cat$year)

ideo_cat <- ideo_cat %>% rename(group = key) 
ideo_cat$group <- gsub("[0-9]*", "", ideo_cat$group)
ideo_cat$group <- gsub("_", "", ideo_cat$group)
ideo_cat$group <- as.factor(ideo_cat$group) 
ideo_cat$group <- dplyr::recode(ideo_cat$group, "GCC" = "Greek-Cypriots", "TCC" = "Turkish-Cypriots")

save(ideo_cat, file=("ideo_cat.rdata"))
load("ideo_cat.rdata")
```



```{r include=FALSE}

library(dplyr)
library(plotly)
library(ggplot2)

load("/Users/Yioryos/Career/Cyprus blog/Data/Cyprus/Data/ideo_cat.rdata")
load("/Users/Yioryos/Career/Cyprus blog/Data/Cyprus/Data/ideology_eu.rdata")
load("/Users/Yioryos/Career/Cyprus blog/Data/Cyprus/Data/ideology_gen.rdata")

#####Plots

#Analysis 1: Divergent lollipop plot of left-right ideology mean in 2018, Cyprus and EU

ideology_eu <- ideology_eu %>% #Sorting for ggplot
  arrange(ideology) %>%
  mutate(group = factor(group, levels = .$group))

cyp <- subset(ideology_eu, group == "Cyprus (GCC & TCC)")

plot_ideology_eu <- ggplot(ideology_eu, aes(x=group, y=ideology, label=ideology)) + 
  geom_point(stat='identity', fill="black", size=6)  +
  geom_point(data=cyp, colour="#9702A7", size=6) +
  geom_segment(aes(y = 5, 
                   x = group, 
                   yend = ideology, 
                   xend = group), 
               color = "black") +
  geom_text(color="white", size=3) +
  labs(title="Ideological Self-Identification in EU (2018)", 
       subtitle = "Eurobarometer 90.3",
       caption="www.c-pot.org",
       y = "Left-Right Placement (1 = left, 10 = right)", x = "") + 
  scale_y_continuous(breaks=seq(2,8,1), limits=c(2,8)) +
  coord_flip() +
  theme(plot.caption = element_text(size = 10, margin = margin(t = 10), color = "grey40", hjust = 0))



#Analysis 2: Bar chart for left-right ideology by gender in Cyprus and EU-28

ideology_gen <- ideology_gen %>% #Sorting to display correct standard errors in plotly bar chart
  arrange(gender)

#Legend attributes
l <- list(font = list(family = "arial", size = 18, color = "#000"), x = 100, y = 0.5, traceorder="reversed")

#Annotation (individual title) attributes
anot_ideo <- list(
  text = "Ideological Self-Identification (2018)",
  font = list(family = "avenir", size = 22, color = "#484848"),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = .98,
  showarrow = FALSE
)

anot_logo <- list(
  text = "www.c-pot.org",
  font = list(family = "avenir", size = 17, color = "#484848"),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "bottom",
  align = "right",
  x = 1.25,
  y = 0.27,
  showarrow = FALSE
)



plot_ideology_gen <- plot_ly(ideology_gen, size = I(35)) %>%
  add_bars(
    y = ~group, yend = ~group,
    x = ~ideology, xend = 0,
    color = ~gender,
    error_x = list(
      type = "ideology_gen", 
      array = ~se,
      thickness = 2,
      width = 4,
      color = "black"))  %>%
  layout(yaxis = list(title = ""),
         xaxis = list(title = "Left-Right Placement (1 = left, 10 = right)", dtick = 1, tickfont = list(size = 15), range = c(1,7)),
         legend = l,
         annotations = list(anot_ideo, anot_logo))


#Analysis 3: Plot for left-right ideology categories over time in Cyprus

ideo_cat_gcc <- ideo_cat %>% filter(group == "Greek-Cypriots")
ideo_cat_tcc <- ideo_cat %>% filter(group == "Turkish-Cypriots")

#Legend attributes
l <- list(font = list(family = "arial", size = 18, color = "#000"), x = 100, y = 0.5, traceorder="reversed")

#Annotation (individual title) attributes
anot_ideo_cat_gcc <- list(
  text = "Greek-Cypriots",
  font = list(family = "avenir", size = 18, color = "#484848"),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.52,
  y = .91,
  showarrow = FALSE
)

anot_ideo_cat_tcc <- list(
  text = "Turkish-Cypriots",
  font = list(family = "avenir", size = 18, color = "#484848"),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.52,
  y = .91,
  showarrow = FALSE
)

anot_ideo_cat <- list(
  text = "Ideological Self-Identification",
  font = list(family = "avenir", size = 20, color = "#484848"),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "center",
  align = "center",
  x = 0.5,
  y = .98,
  showarrow = FALSE
)



anot_logo <- list(
  text = "www.c-pot.org",
  font = list(family = "avenir", size = 18, color = "#484848"),
  xref = "paper",
  yref = "paper",
  yanchor = "bottom",
  xanchor = "bottom",
  align = "right",
  x = 1.22,
  y = 0.15,
  showarrow = FALSE
)

pal <- c("#bbbbbb","#228833","#ee6677","#4477aa")

plot_ideo_cat_gcc <- plot_ly(ideo_cat_gcc, y = ~value, x= ~year, 
                             color = ~ideology, colors = pal, 
                             type = "scatter",
                             mode = "lines+markers", 
                             line = list(width = 3), 
                             marker = list(size = 5),
                             legendgroup = ~ideology, showlegend = T) %>% 
  layout(yaxis = list(title = "Percent", titlefont=list(size=18), range = c(0,60), tickfont = list(size = 16)),
         xaxis = list(title = "", dtick = 2, tickfont = list(size = 16), tickangle = 45),
         legend = l, 
         annotations = list(anot_ideo_cat_gcc))

plot_ideo_cat_tcc <- plot_ly(ideo_cat_tcc, y = ~value, x= ~year, 
                             color = ~ideology, colors = pal, 
                             type = "scatter",
                             mode = "lines+markers", 
                             line = list(width = 3), 
                             marker = list(size = 5),
                             legendgroup = ~ideology, showlegend = F) %>% 
  layout(yaxis = list(title = "Percent", titlefont=list(size=18), range = c(0,60), tickfont = list(size = 16)),
         xaxis = list(title = "", dtick = 2, tickfont = list(size = 16), tickangle = 45),
         legend = l,
         annotations = list(anot_ideo_cat_tcc))

#Combining plots for Cypriots
plot_ideo_cat <- plotly::subplot(plot_ideo_cat_gcc, plot_ideo_cat_tcc, 
                                             nrows = 1, margin = 0.04, shareX = F, shareY = T, 
                                             titleY = TRUE) %>% 
  layout(annotations = list(anot_ideo_cat, anot_logo), autosize = F, width = 920, height = 600) 

```

<br>

>How do Cypriots classify their political ideologies and preferences? To what extent do they identify with the notions of the "left" and "right"?  
• In general, Turkish-Cypriots are more likely to identify with the left or right than Greek-Cypriots. In turn, Greek-Cypriots are more likely to identify with the centre or to not express a preference than Turkish-Cypriots.  
• The proportion of Cypriots that do not express a preference has gone from being the least common to the most common preference between 2004-2018.  
• Cypriots on average are more to the right than most of the EU. Greek-Cypriot women tend to be more to the right than men, whereas in the EU overall, men are more to the right than women.
<br><br>
__Η Ιδεολογική Ταυτότητα στην Κύπρο__  
Πώς κατατάσσουν οι Κύπριοι τις πολιτικές ιδεολογίες και προτιμήσεις τους; Σε ποιο βαθμό ταυτίζονται με τις αντιλήψεις της "αριστεράς" και της "δεξιάς";   
• Σε γενικές γραμμές, οι Τουρκοκύπριοι ταυτίζονται με τις αντιλήψεις της αριστεράς ή της δεξιάς σε πιο ψηλά ποσοστά απ' ό,τι οι Ελληνοκύπριοι.  Οι Ελληνοκύπριοι ταυτίζονται με τις αντιλήψεις του κέντρου ή δεν εκφέρουν προτίμηση σε ψηλότερα επίπεδα απ' ό,τι οι Τουρκοκύπριοι.   
• Το ποσοστό των Κυπρίων που δεν εκφέρει προτίμηση έχει αυξηθεί από την λιγότερη συχνή τοποθέτηση στην πιο συχνή τοποθέτηση μεταξύ το 2004 και 2018.    
• Οι Κύπριοι τείνουν προς τα δεξιά σε ψηλότερα επίπεδα από το Κοινοτικό μέσο όρο. Οι Ελληνοκύπριες τοποθετούνται προς τα δεξιά περισσότερο απ' ό,τι οι άνδρες, ενώ στην ΕΕ συνολικά, οι άντρες τοποθετούνται προς τα δεξιά περισσότερο απ' ό,τι οι γυναίκες.  
<br><br>
__Kıbrıs'ta İdeolojik Kimlikler__  
• Kıbrıs Türkleri siyasi ideolojilerini ve tercihlerini nasıl tanımlıyorlar? "Sol" ve "sağ" kavramları ile kendilerini ne ölçüde özdeşleştiriyorlar? Kıbrıs Türkleri genel olarak Kıbrıs Rumlarına kıyasla sol veya sağ görüşlere daha yatkınlardır. Öte yandan Kıbrıs Rumları kendilerini çoğunlukla merkezde konumlandırıyorlar veya siyasi bir tercihte bulunmuyorlar.  
• Siyasi görüş belirtmeyen Kıbrıslıların oranı 2004-2018 arasında en nadir rastlanan siyasi tercihten en sık rastlanan siyasi tercihe ilerlemiştir.  
• Kıbrıslılar çoğunlukla Avrupa Birliği’ne nazaran sağa daha yatkınlardır. Kıbrıslı Rum kadınlar erkeklere göre sağ görüşlere sahipken Avrupa Birliği’nde erkekler genellikle kadınlara göre sağ görüşlere daha meyillilerdir.  

<br>
How do Cypriots classify their political ideologies and preferences? To what extent do they identify with the notions of the "left" and "right"?  
<br>
To explore this we use Eurobarometer survey questions from 2004-2018 that ask respondents to place themselves on a 10-point scale where '1' represents the left and '10' represents the right. First we consider the extent to which Cypriots identify with the left and right over time. The Eurobarometer considers responses from '1'-'4' as  'left', '5'-'6' as 'centre', and '7'-'10' as 'right'. Then we'll examine average scores on the 10-point scale to get a sense of how it compares to the rest of the EU.  
<br>
The results show that in most years, Turkish-Cypriots are more likely to identify with the left or right than Greek-Cypriots. In turn, Greek-Cypriots are more likely to identify with the centre or to not express a preference (i.e. say they don't know) than Turkish-Cypriots. Among Greek-Cypriots, the proportion that identifies with the left has declined the most during this time period, while the proportion that does not express a preference has increased substantially.  
<br>
In fact, the lack of an ideological preference has become increasingly common among all Cypriots, as more recently it has risen among Turkish-Cypriots as well. The proportion of Cypriots that do not express a preference has gone from being the least common to the most common preference over this time period. This may reflect the increasing disillusionment with politics in Cyprus discussed in the first two blog posts, and again particularly for Greek-Cypriots.
<br><br>
`r plot_ideo_cat`
<br><br><br><br><br><br><br><br>
Note: no data For Turkish-Cypriots in 2012 & 2013.
<br><br>
_Interactive visualizations: hover over to display values, double-click to zoom, click legend to hide/show specific lines_<br><br><br>

Despite these differences in ideological preferences, the most recent 2018 data show that among people that do identify with an ideological position (as opposed to those that say they don't know), the average score of Greek-Cypriots and Turkish-Cypriots on the 10-point left-right scale is quite similar. Greek-Cypriot women are more to the right than men, whereas in the EU overall, men tend to be more to the right than women.  
<br>
Cypriots on average are more to the right than most of the EU. Cypriots' average placement on the 10-point scale is 5.5, whereas the EU-28 score is 5.1. Out of 28 countries, Cypriots rank 6th (along with Slovakia and Romania) on the left-right continuum. 
<br><br>
`r plot_ideology_gen`
<br><br>
 
```{r echo=FALSE}

plot_ideology_eu
```
<br><br>
__Data sources__  
Eurobarometer: 62, 63.4, 65.2, 68.1, 70.1, 71.3, 74.2, 75.3, 81.4, 84.3, 85.2, 87.3, 90.3  



